Preregistration analysis, Cost 2 study

### 2019-05-13 Cost2/Cost2_prereg.Rmd
further matching the corrplots across studies

The plot below shows the distribution of random intercepts across participants of each group. Participants in the easy condition show much more variability than the other groups, potentially suggesting a bias in choices in this condition. Nonetheless, the intercepts per group are centered around zero.

@@

# plot per subject (as expected, the intercepts are highest for those who accepted everythiing)
temp <- ranef(mixLogis_main$Wait)$SubjID %>%
  gather(key = Cost, value = RandEffects, colnames(.))

(RI1 <- ggplot(data = temp, aes(Cost, RandEffects, fill = Cost)) + 
  geom_hline(yintercept = 0, alpha = 0.7, linetype = "dashed") + 
  geom_boxplot(show.legend = F) +
  scale_fill_manual(values = cols) + 
  labs(x = "") +
  theme(panel.grid.major = element_blank(), 
              panel.grid.minor = element_blank(), 
              panel.background = element_blank(), 
              axis.line = element_line(colour = "black"),
              text = element_text(size = 16)))

>>>>

@@

# # plot per subject (as expected, the intercepts are highest for those who accepted everythiing)
# temp <- ranef(mixLogis_main$Wait)$SubjID %>%
#   gather(key = Cost, value = RandEffects, colnames(.)) 
# 
# (RI1 <- ggplot(data = temp, aes(Cost, RandEffects, fill = Cost)) + 
#   geom_hline(yintercept = 0, alpha = 0.7, linetype = "dashed") + 
#   geom_boxplot(show.legend = F) +
#   scale_fill_manual(values = cols) + 
#   labs(x = "") +
#   theme(panel.grid.major = element_blank(), 
#               panel.grid.minor = element_blank(), 
#               panel.background = element_blank(), 
#               axis.line = element_line(colour = "black"),
#               text = element_text(size = 16)))
